State Size and City Growth: \\Evidence from Dynastic Takeovers

### 2023-02-19 paper/paper.tex
update intro and references

motivation for effects of size

>>>>

The political history of Europe, until fairly recently, was defined by ruling families passing their territorial holdings down in hereditary monarchies. Land and cities changed hands often throughout the history of Europe. Which territory a city belonged to had economic as well as political consequences, and it is not hard to imagine that the fortunes of whole stretches of land could be decided by such dynastic takeovers. For example, (good example of a takeover and its consequences here).

In this paper I investigate changes in territory size as one possible channel through which dynastic takeovers could affect development. There exists a literature on the optimal size of state (e.g. \cite{as1997}, \cite{aw1998}, \cite{asw2000}, \cite{easterly2000}). This literature focuses on the tradeoffs between scale effects in government on one hand and conflict on the other, as well as trade and openness.
